---
title: "Task 04"
author: "klesto"
date: "2023-12-05"
output: html_document
---

## Task 4. Functions

Create the next functions and test them with a few different arguments:
  
1. Function `above(x, n)` which returns all items of vector `x` that more than `n`. By default `n = 10`. For instance, `above(c(3, 5, 6), 5)` returns `6`.
```{r}
above <- function(x, n = 10) {
  return(x[x > n])
}
```
Test the function with different arguments
```{r}
# Test 1
result1 <- above(c(9, 12, 7), 8)
print(result1)

# Test 2 
result2 <- above(c(3, 5), 4)
print(result2)

# Test 3 (using the default value of n)
result3 <- above(c(8, 12, 15, 3, 6))
print(result3)
```
2. Function `my_ifelse(x, exp, n)` which compares all items of vector `x` with `n` using expression `exp`. `exp` can be `<`, `<=`, `>`, `>=`, `==`. For instance, `exp(c(3, 5, 6), ">=", 5)` returns `5, 6`.
my_ifelse <- function(x, exp, n) {
```{r}
my_ifelse <- function(x, exp, n) {
  # Check the expression and perform the comparison
  if (exp == "<") {
    return(x[x < n])
  } else if (exp == "<=") {
    return(x[x <= n])
  } else if (exp == ">") {
    return(x[x > n])
  } else if (exp == ">=") {
    return(x[x >= n])
  } else if (exp == "==") {
    return(x[x == n])
  }
}
```
Test the function with different arguments
```{r}
test_vector1 <- c(3, 5, 6)
result1 <- my_ifelse(test_vector1, "==", 5)
print(result1)

test_vector2 <- c(8, 10, 12, 15, 4, 20, 2)
result2 <- my_ifelse(test_vector2, ">=", 10)
print(result2)

test_vector3 <- c(2, 3, 7, 12)
result3 <- my_ifelse(test_vector3, ">", 7)
print(result3)

test_vector4 <- c(5, 9, 22, 1, 8, 3, 11)
result4 <- my_ifelse(test_vector4, "<=", 8)
print(result4)

test_vector5 <- c(2, 3, 7, 12)
result5 <- my_ifelse(test_vector5, "<", 7)
print(result5)

# Test with random vector 

random_vector <- rnorm(10)
result6 <- my_ifelse(random_vector, ">", 1)
print(random_vector)
print(result6)
```
3. Function `my_columnmean(df, removeNA)` that returns mean value for each column of data frame or matrix `df`. Logical argument `removeNA` set whether remove NA values or not. By default `removeNA = True`. Use loop `for` of `while` for the function.
```{r}
my_columnmean <- function(df, removeNA = TRUE) {
  column_count <- ncol(df)
  mean_vector <- numeric(column_count)  # Initialize a vector to store the mean values
  
  while (column_count > 0) {
    current_column <- df[, column_count]
    
    if (removeNA) {
      current_column <- current_column[!is.na(current_column)]
    }
    
    if (length(current_column) > 0) {
      mean_vector[column_count] <- mean(current_column)
    } else {
      mean_vector[column_count] <- NA
    }
    
    column_count <- column_count - 1
  }
  
  return(mean_vector)
}

# Test the function with different arguments
# Test case 1
df1 <- data.frame(a = c(1, 2, NA, 4, 5, 6), b = c(NA, 2, 3, 4, 5, 6))
result1 <- my_columnmean(df1)
cat("Test Case 1:", result1, "\n")

# Test case 2 (with removeNA = FALSE)
df2 <- data.frame(a = c(1, 2, NA, 4, 5, 6), b = c(NA, 2, 3, 4, 5, 6))
result2 <- my_columnmean(df2, removeNA = FALSE)
cat("Test Case 2:", result2, "\n")

# Test case 3 (with a matrix)
mat <- matrix(c(1, 2, 3, NA, 5, 6), ncol = 2)
result3 <- my_columnmean(mat)
cat("Test Case 3:", result3, "\n")
```
