---
title: "Task 04"
author: "klesto"
date: "2023-12-05"
output: html_document
---

## Task 4. Functions

Create the next functions and test them with a few different arguments:

1. Function `above(x, n)` which returns all items of vector `x` that more than `n`. By default `n = 10`. For instance, `above(c(3, 5, 6), 5)` returns `6`.
```{r}
above <- function(x, n = 10) {
  return(x[x > n])
}

# Test the function with different arguments
test_vector1 <- c(3, 5, 6)
result1 <- above(test_vector1, 5)
cat("Test 1 Result:", result1, "\n")

test_vector2 <- c(8, 12, 15, 4, 20)
result2 <- above(test_vector2)
cat("Test 2 Result:", result2, "\n")

test_vector3 <- c(2, 3, 7, 12)
result3 <- above(test_vector3, 8)
cat("Test 3 Result:", result3, "\n")
```
2. Function `my_ifelse(x, exp, n)` which compares all items of vector `x` with `n` using expression `exp`. `exp` can be `<`, `<=`, `>`, `>=`, `==`. For instance, `exp(c(3, 5, 6), ">=", 5)` returns `5, 6`.
my_ifelse <- function(x, exp, n) {
```{r}
my_ifelse <- function(x, exp, n) {
  # Check the expression and perform the comparison
  if (exp == "<") {
    return(x[x < n])
  } else if (exp == "<=") {
    return(x[x <= n])
  } else if (exp == ">") {
    return(x[x > n])
  } else if (exp == ">=") {
    return(x[x >= n])
  } else if (exp == "==") {
    return(x[x == n])
  } else {
    stop("Invalid expression. Use '<', '<=', '>', '>=', or '=='")
  }
}

# Test the function with different arguments
test_vector1 <- c(3, 5, 6)
result1 <- my_ifelse(test_vector1, ">=", 5)
cat("Test 1 Result:", result1, "\n")

test_vector2 <- c(8, 12, 15, 4, 20)
result2 <- my_ifelse(test_vector2, "<", 10)
cat("Test 2 Result:", result2, "\n")

test_vector3 <- c(2, 3, 7, 12)
result3 <- my_ifelse(test_vector3, "==", 7)
cat("Test 3 Result:", result3, "\n")

```
3. Function `my_columnmean(df, removeNA)` that returns mean value for each column of data frame or matrix `df`. Logical argument `removeNA` set whether remove NA values or not. By default `removeNA = True`. Use loop `for` of `while` for the function.
```{r}

```