---
title: "Task 04"
author: "klesto"
date: "2023-12-05"
output: html_document
---

## Task 4. Functions

Create the next functions and test them with a few different arguments:

1. Function `above(x, n)` which returns all items of vector `x` that more than `n`. By default `n = 10`. For instance, `above(c(3, 5, 6), 5)` returns `6`.
```{r}
above <- function(x, n = 10) {
  return(x[x > n])
}

# Test the function
above(c(3, 5, 6), 5)
above(c(8, 12, 15, 3, 6), 10)
above(c(1, 2, 3, 4, 5), 3)
```
2. Function `my_ifelse(x, exp, n)` which compares all items of vector `x` with `n` using expression `exp`. `exp` can be `<`, `<=`, `>`, `>=`, `==`. For instance, `exp(c(3, 5, 6), ">=", 5)` returns `5, 6`.
my_ifelse <- function(x, exp, n) {
```{r}
my_ifelse <- function(x, exp, n) {
  comparison <- switch(exp,
                       "<" = x[x < n],
                       "<=" = x[x <= n],
                       ">" = x[x > n],
                       ">=" = x[x >= n],
                       "==" = x[x == n],
                       stop("Invalid comparison expression. Use '<', '<=', '>', '>=', or '=='."))

  return(comparison)
}

# Test the function
my_ifelse(c(3, 5, 6), ">=", 5)
my_ifelse(c(8, 12, 15, 3, 6), "<", 10)
my_ifelse(c(1, 2, 3, 4, 5), "==", 3)
```
3. Function `my_columnmean(df, removeNA)` that returns mean value for each column of data frame or matrix `df`. Logical argument `removeNA` set whether remove NA values or not. By default `removeNA = True`. Use loop `for` of `while` for the function.
```{r}
my_columnmean <- function(df, removeNA = TRUE) {
  num_cols <- ncol(df)
  means <- numeric(num_cols)

  for (i in 1:num_cols) {
    col_values <- df[, i]
    if (removeNA) {
      col_values <- col_values[!is.na(col_values)]
    }
    means[i] <- mean(col_values)
  }

  return(means)
}

# Test the function
df <- data.frame(a = c(1, 2, 3, NA, 5),
                 b = c(6, 7, 8, 9, 10))

my_columnmean(df)
my_columnmean(df, removeNA = FALSE)
```