---
title: "Lab 1"
author: "Matej Klestinec"
date: "2023-10-23"
output: html_document
---

# Task 1

## 1 Create variables with all atomic types. Atomic types: character, numeric, integer, complex, logical.

Numeric
```{r}
y<-2.8
class(y)
y
x<-22
class(x)
x
```
Character
```{r}
w<-c("Hello, how are you")
class(w)
w
```
Integer
```{r}
f<-as.integer(22)
class(f)
f
```
Complex
```{r}
z<-1 + 2i
class(z)
z
```
Logical
```{r}
logical<-as.logical(FALSE)
class(logical)
logical
```
## 2 Create the next vectors:
sequence from 5 to 75;
```{R}
s<-5:75
s
```
numbers: 3.14, 2.71, 0, 13;
```{R}
n<-c(3.14, 2.71, 0, 13)
n
```
with 100 TRUE values. DOROBIT
```{R}
```
## Create the next matrix:
```{R}
A = matrix(c(12, 34, 87, -12, -12.1, 0, 3.6, 0.5, 1.3), 
  nrow=3,
  ncol=3,
  byrow = TRUE
)
  rownames(A) = c("a", "b", "c")
  colnames(A) = c("c", "d", "e")
  
print(A)
```
## Create a list with all atomic types.
```{R}
list(y, x, w, f, z, logical, s, A)
```
## Create a factor with 3 levels: infant, child, adult.
```{R}
age<-c("infant", "child", "adult")
print(age)
levels(age)["infant"] <- 1
levels(age)["child"] <- 2
levels(age)["adult"] <- 3
levels(age)
```
## Create a data frame
```{R}
column1 <- c("Matej", "Peter")
column2 <- c("21", "60")
df1 <- data.frame(column1, column2)
print(df1)
```
## Change column names of the data frame.
```{R}
colnames(df1) <- c('Name', 'Age')
print(df1)
```