---
title: "Task 2"
author: "Matej Klestinec"
date: "2023-10-23"
output: html_document
---

# Task 2

## Exploring a dataset

0. **Load the dataset**
```{r}
airquality_dataset <- read.csv("airquality.csv")
```

1.  **What are the column names of the data frame?**

```{r}
colnames(airquality_dataset)
```
2.  **What are the row names of the data frame?**

```{r}
rownames(airquality_dataset)
```
3.  **Extract the first 6 rows of the data frame and print them to the console**

```{r}
# head function extracts data from the beginning
head(airquality_dataset, 6)
```

4.  **How many observations (i.e. rows) are in this data frame?**
```{r}
# nrow function counts the number of rows in the dataset
nrow(airquality_dataset)
```

5.  **Extract the last 6 rows of the data frame and print them to the console**

```{r}
# tail function extracts data from the end
tail(airquality_dataset, 6)
```

6.  **How many missing values are in the "Ozone" column of this data frame?**
```{r}
# "is.na" function is used to create a logical vector "missing_values_ozone" with missing values in the "Ozone" column and then uses the sum function to count the number of TRUE values 
missing_values_ozone <- sum(is.na(airquality_dataset$Ozone))

missing_values_ozone
```
7.  **What is the mean of the "Ozone" column in this dataset? Exclude missing values (coded as NA) from this calculation.**

```{r}
#mean function with the "na.rm = TRUE" parameter to calculate the mean of the "Ozone" column while excluding missing values.
mean_ozone <- mean(airquality_dataset$Ozone, na.rm = TRUE)

mean_ozone
```

8.  **Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90.**

```{r}
### This code uses indexing to subset the rows based on the specified conditions (Ozone > 31 and Temp > 90)
subset_dataset <- airquality_dataset[airquality_dataset$Ozone > 31 & airquality_dataset$Temp > 90, ]

# Display the subset of rows
subset_dataset
```
